\textcolor{red}{Testing with Graphs}

### 2019-02-08 notes/graph_testing.tex
added notes for this week

%%% Functionals
\newcommand{\1}{\mathbf{1}}
\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

@@

Our test statistics $T_1(\lbf; G_{n,r})$ and $T_2(\lbf; G_{n,r})$ are defined as follows:
\begin{align*}
	T_1(\lbf; G_{n,r}) := \sup_{\fbf \in \Reals^n: \norm{\Bbf \fbf}_1 \leq C_{n,r}} ~ \frac{1}{n} \sum_{k = 1}^{n} \ell_k f_k \\
	T_2(\lbf; G_{n,r}) := \sup_{\fbf \in \Reals^n: \norm{\Bbf \fbf}_2^2 \leq C_{n,r}} ~ \frac{1}{n} \sum_{k = 1}^{n} \ell_k f_k
\end{align*}
where \textcolor{red}{$C_{n,r} = $} and we write $\fbf = (f_1,\ldots, f_n)$. We note that, as promised, these satisfy the form
\begin{align*}
T_1(\lbf; G_{n,r}) & = \sup_{f_n \in TV_n}\abs{\int_{D} f_n d\Pbb_n - \int_{D} f_n d\Qbb_n} \\
T_2(\lbf; G_{n,r}) & = \sup_{f_n \in \Wset_n}\abs{\int_{D} f_n d\Pbb_n - \int_{D} f_n d\Qbb_n}
\end{align*}
where $TV_n = \set{\fbf: \norm{\Bbf \fbf}_1 \leq C_{n,r}}$ and $\Wset_n = \set{\fbf: \norm{\Bbf \fbf}_2 \leq C_{n,r}}$.

@@

\begin{theorem}
	\label{thm: LLN_for_t2}
	Let $d \geq 2$ and let $\Dset \subset \Rd$ be an open, bounded, connected set with Lipschitz boundary. Let $\mu$ satisfy
	\begin{equation*}
	m \leq \mu(x) \leq M \tag{$\forall x \in D$}
	\end{equation*}
	for some $0 < m \leq M$. Let $(r_n)$ be a sequence of positive numbers converging to $0$ and satisfying
	\begin{align*}
	& \lim_{n \to \infty} \frac{(\log n)^{3/4}}{n^{1/2}} \frac{1}{r_n} = 0 ~~ \text{if $d = 2$} \\
	& \lim_{n \to \infty} \frac{(\log n)^{1/d}}{n^{1/d}} \frac{1}{r_n} = 0 ~~ \text{if $d \geq 3$}
	\end{align*}
	Assume the kernel $k$ satisfies conditions: 
	\begin{align*}
	& k(0) > 0 ~ \text{and $k$ is continuous at $0$.} \tag{\textbf{K1}} \\
	& k~ \text{is non-increasing.} \tag{\textbf{K2}} \\
	& \text{The integral $\int_{0}^{\infty} k(r) r^{d+1} dr$ is finite.} \tag{\textbf{K3}}
	\end{align*}

	Then with probability one the following statement holds: For $(z_1, \ldots, z_n)$ chosen under the binomialized data model
	\begin{equation*}
	\lim_{n \to \infty} T_2(\lbf; G_{n,r_n}) = \gamma_{\Wset^{1,2}(\Dset,\mu^2)}(\Pbb,\Qbb).
	\end{equation*}
\end{theorem}

@@

\begin{theorem}[Theorem 1.4 of \cite{trillos2018}]
	Under the setup and conditions of Theorem \ref{thm: LLN_for_t2}, with probability one the following statements hold:
	\begin{itemize}
		\item \emph{Liminf inequality:}
		For all $f \in L^2(\mu)$ and all sequences $(f_n)$ with $f_n \in L^2(\mu_n)$ and $f_n \overset{TL^2}{\to} f$,
		\begin{equation*}
		\liminf_{n \to \infty} \frac{1}{n^2 r_n^{d + 2}} \norm{Bf}_2^2 \geq \textcolor{red}{\sigma_{k}} \norm{f}_{1,2,\rho^2}
		\end{equation*}

		\item \emph{Limsup inequality:} For all $f \in L^2(\mu)$, there exists a sequence $(f_n)$ with $f_n \in L^2(\mu_n)$ and $f_n \overset{TL^2}{\to} f$ such that
		\begin{equation*}
		\limsup_{n \to \infty} \frac{1}{n^2 r_n^{d + 2}} \norm{Bf}_2^2 \leq \textcolor{red}{\sigma_{k}} \norm{f}_{1,2,\rho^2}
		\end{equation*}

@@

@@

>>>>

%%% Functionals
\newcommand{\1}{\mathbf{1}}

\newtheoremstyle{alden}
{6pt} % Space above
{6pt} % Space below
{} % Body font
{} % Indent amount
{\bfseries} % Theorem head font
{.} % Punctuation after theorem head
{.5em} % Space after theorem head
{} % Theorem head spec (can be left empty, meaning `normal')

@@

Our test statistics $T_1(\lbf; G_{n,r})$ and $T_2(\lbf; G_{n,r})$ are defined as follows:
\begin{align*}
	T_1(\lbf; G_{n,r}) := \sup_{\fbf \in \Reals^n: \norm{\Bbf \fbf}_1 \leq C_{n,r}} ~ \frac{1}{n} \sum_{k = 1}^{n} \ell_k f_k \\
	T_2(\lbf; G_{n,r}) := \sup_{\fbf \in \Reals^n: \norm{\Bbf \fbf}_2^2 \leq C_{n,r}} ~ \frac{1}{n} \sum_{k = 1}^{n} \ell_k f_k
\end{align*}
where $C_{n,r} = \frac{\sigma_k}{n^2 r_n^{d+2}}$ and we write $\fbf = (f_1,\ldots, f_n)$. We note that, as promised, these satisfy the form
\begin{align*}
T_1(\lbf; G_{n,r}) & = \sup_{f_n \in TV_n}\abs{\int_{D} f_n d\Pbb_n - \int_{D} f_n d\Qbb_n} \\
T_2(\lbf; G_{n,r}) & = \sup_{f_n \in \Wset_n}\abs{\int_{D} f_n d\Pbb_n - \int_{D} f_n d\Qbb_n}
\end{align*}
where $TV_n = \set{\fbf: \norm{\Bbf \fbf}_1 \leq C_{n,r}}$ and $\Wset_n = \set{\fbf: \norm{\Bbf \fbf}_2 \leq C_{n,r}}$.

@@

\begin{theorem}[Pointwise limit of Laplacian smooth test statistic.]
	\label{thm: LLN_for_t2}
	Let $d \geq 2$ and let $\Dset \subset \Rd$ be an open, bounded, connected set with Lipschitz boundary. Let $\mu$ satisfy
	\begin{equation*}
	m \leq \mu(x) \leq M \tag{$\forall x \in D$}
	\end{equation*}
	for some $0 < m \leq M$. Let $(r_n)$ be a sequence of positive numbers converging to $0$ and satisfying
	\begin{align*}
	& \lim_{n \to \infty} \frac{(\log n)^{3/4}}{n^{1/2}} \frac{1}{r_n} = 0 ~~ \text{if $d = 2$} \\
	& \lim_{n \to \infty} \frac{(\log n)^{1/d}}{n^{1/d}} \frac{1}{r_n} = 0 ~~ \text{if $d \geq 3$}
	\end{align*}
	Assume the kernel $k$ satisfies conditions: 
	\begin{align*}
	& k(0) > 0 ~ \text{and $k$ is continuous at $0$.} \tag{\textbf{K1}} \\
	& k~ \text{is non-increasing.} \tag{\textbf{K2}} \\
	& \text{The integral $\int_{0}^{\infty} k(r) r^{d+1} dr$ is finite.} \tag{\textbf{K3}}
	\end{align*}

	Then with probability one the following statement holds: For $(z_1, \ldots, z_n)$ chosen under the binomialized data model,
	\begin{equation*}
	\lim_{n \to \infty} T_2(\lbf; G_{n,r_n}) = \gamma_{\Wset^{1,2}(\Dset,\mu^2)}(\Pbb,\Qbb).
	\end{equation*}
\end{theorem}

@@

\begin{theorem}[Theorem 1.4 of \cite{trillos2018}]
	\label{thm: gamma_convergence_energy_functional}
	Under the setup and conditions of Theorem \ref{thm: LLN_for_t2}, with probability one the following statements hold:
	\begin{itemize}
		\item \emph{Liminf inequality:}
		For all $f \in L^2(\mu)$ and all sequences $(f_n)$ with $f_n \in L^2(\mu_n)$ and $f_n \overset{TL^2}{\to} f$,
		\begin{equation*}
		\liminf_{n \to \infty} \frac{1}{n^2 r_n^{d + 2}} \norm{Bf}_2^2 \geq \textcolor{red}{\sigma_{k}} \norm{f}_{1,2,\rho^2}
		\end{equation*}

		\item \emph{Limsup inequality:} For all $f \in L^2(\mu)$, there exists a sequence $(f_n)$ with $f_n \in L^2(\mu_n)$ and $f_n \overset{TL^2}{\to} f$ such that
		\begin{equation*}
		\limsup_{n \to \infty} \frac{1}{n^2 r_n^{d + 2}} \norm{\Bbf \fbf_n }_2^2 \leq \textcolor{red}{\sigma_{k}} \norm{f}_{1,2,\rho^2}
		\end{equation*}
		where $\fbf_n = (f_n(z_1), \ldots, f_n(z_n))$.

@@

\begin{lemma}
	\label{lem: continuity_of_risk_functional}
	With probability one the following statement holds: If a sequence $(f_n)$ where $f_n: \set{z_1, \ldots,z_n} \to [-1,1]^{n}$ converges $TL^2$ to $f \in L^2(\mu)$, then
	\begin{equation*}
	\lim_{n \to \infty} \frac{1}{n} \sum_{k = 1}^{n} \ell_k f_n(z_k) = \int_{\Dset} f d\Pbb(x) - \int_{\Dset} fd\Qbb(x).
 	\end{equation*}
\end{lemma}

@@

Let $f^{\star}$ be the witness function for $\gamma_{\Wset^{1,2}(\Dset,\mu^2)}(\Pbb,\Qbb)$, meaning
\begin{equation*}
\abs{\int_{\Dset}f^{\star}d\Pbb - \int_{\Dset}f^{\star}d\Qbb} = \gamma_{\Wset^{1,2}(\Dset,\mu^2)}(\Pbb,\Qbb)
\end{equation*}
where $f^{\star} \in \Wset^{1,2}(\Dset,\mu^2)$ implies $f^{\star} \in L^2(\mu)$. By the limsup inequality in Theorem \ref{thm: gamma_convergence_energy_functional}, there exists some $(f_n) \overset{TL^2}{\to} f$ with $f_n \in L^2(\mu_n)$ such that
\begin{equation}
\label{eqn: limsup_discrete_energy}
\limsup_{n \to \infty} \frac{1}{n^2 r_n^{d+2}} \norm{\Bbf \fbf_n}_2^2 \leq \textcolor{red}{\sigma_k} \norm{f}_{1,2,\mu^2} \leq \sigma_k.
\end{equation} 
From Lemma \ref{lem: continuity_of_risk_functional}
\begin{equation*}
\lim_{n \to \infty} \frac{1}{n} \sum_{k = 1}^{n} \ell_k f_n(z_k) = \int_{\Dset} f d\Pbb(x) - \int_{\Dset} f d\Qbb(x) = \gamma_{\Wset^{1,2}(\Dset,\mu^2)}.
\end{equation*}
and along with \eqref{eqn: limsup_discrete_energy}, this implies
\begin{equation*}
\lim_{n \to \infty} T_2(\lbf; G_{n,r}) \leq \gamma_{\Wset^{1,2}(\Dset,\mu^2)}(\Pbb,\Qbb).
\end{equation*}

Let $\Lbf^{\dagger}$ be the pseudoinverse of the Laplacian matrix $\Lbf$. We introduce $f_n^{\star} = \lbf^T \Lbf^{\dagger} \lbf$, which satisfies
\begin{equation*}
\abs{\int_{\Dset}f_n^{\star}d\Pbb_n - \int_{\Dset}f_n^{\star}d\Qbb_n} = T_2(\lbf; G_{n,r})
\end{equation*}
Note that
\begin{equation*}
\norm{\Bbf \fbf_n^{\star}}_2^2 \leq C_n \Longrightarrow \frac{1}{n^2 r_n^{d+2}} \norm{\Bbf \fbf_n^{\star}}_2^2  \leq \sigma_k < \infty
\end{equation*}
and so by the compactness property in Theorem \ref{thm: gamma_convergence_energy_functional}, every subsequence of $f_n^{\star}$ has a further subsequence which is $TL^2$-convergent. For simplicity, and without loss of generality, let us work along a subsequence which is convergent (and call it $f_n^{\star}$) to $f \in L^2(\mu)$. Then
\begin{equation}
\label{eqn: lower_bound_T2_1}
\lim_{n \to \infty} \frac{1}{n} \sum_{k = 1}^{n} \ell_k f_n^{\star}(z_k) = \abs{\int_{\Dset}f d\Pbb(x) - \int_{\Dset}f d\Qbb(x)}
\end{equation}
and by the liminf inequality of Theorem \ref{thm: gamma_convergence_energy_functional},
\begin{equation*}
\liminf_{n \to \infty} \frac{1}{n^2 r_n^{d+2}} \norm{\Bbf \fbf_n}_2^2 \geq \sigma_k \norm{f}_{1,2,\mu^2}
\end{equation*}
which implies $\norm{f}_{1,2,\mu^2} \leq 1$. This, along with \eqref{eqn: lower_bound_T2_1}, implies
\begin{equation*}
\lim_{n \to \infty} \frac{1}{n} \sum_{k = 1}^{n} \ell_k f_n^{\star}(z_k) \geq \gamma_{\Wset^{1,2}(\Dset,\mu^2)}(\Pbb,\Qbb)
\end{equation*}
